---
title: "WUP_04"
author: "Michelle Cervantes"
date: "October 16 2020"
output:
  html_document:
    df_print: paged
---

```{r include=FALSE,echo=FALSE}
require(knitr)
require(tidyverse)
require(tigerstats)
mydata<-read.csv(file="GSScsv.csv")
```

# Introduction

<!--In this section you explain what you are trying to show.  Where did the data come from?  What is the research or other question you are trying to answer?!-->

The data is in the file GSScsv.csv and came from the 2018 General Social Survey.  The question to answer is to resolve this hypothesis.  
$H_0$ There is no difference between the average score on the WORDSUM test and level of schooling DEGREE  
$H_a$ There is a significant difference in average score on the WORDSUM test between at least two levels of DEGREE  

# Methods

<!--Decide on your methods:  use "variable analysis" or other appropriate descriptors.  Make sure to choose at least one graphical method and at least one numerical method.!-->

# Results

<!--Divide this section into two sub-sections:  One for your descriptive  results and one for your inferential results.!-->

## Descriptive Results

### Graphical Descriptive Results

<!--Graphical results here.  Make sure to show your code.  Provide appropriate labels for axes, giving units if possible, and provide a good title for the graph, too.  Use the graphical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
boxplot(WORDSUM~DEGREE,data=mydata)
```

Based on this chart, it shows that a fewer population in the Graduate section were reported however they look like the have a higher average on the WORDSUM. After the Graduates, the Bachelors and some junior college students are tied in their average scores. 

### Numerical Descriptive Results

<!--Numerical results go here. Use the numerical results to describe the patterns if any that exist in the data as focused toward the research question!-->

```{r}
favstats(WORDSUM~DEGREE,data=mydata)
```

This chart summarizes that Graduates have an average of 11 and after that, bachelors and junior college share almost similar results and share the same average of 10. Lastly, LT high school has the lowest average results out of the other groups.

## Inferential Results

<!--State hypothesis clearly.  Make sure your discussion of the inferential test covers all the aspects that the test output produces, such as test statistic, p-value etc.  Make a decision about the null hypothesis, explain the assumptions on which the selected test/procedure was based, and why the chosen procedure satisfys the assumptions and is appropriate to answer the research question!-->

```{r}
model1 <- aov(WORDSUM~DEGREE,data=mydata)
summary.aov(model1)
```


```{r}
plot(TukeyHSD(model1))
```

The p-value we have gathered based on out charts is 0.0002 which tells us the chances of this data appearing the same again are low. This is because two groups here have very different means in their results. Our confidence level chart shows us that high school graduate and LT high school graduate are the most different from the other groups listed which are virtually, statistically the same. 

# Discussion and Conclusion

<!--Discussion and conclusion here.  If you found a relationship be sure to consider whether the relationship occurs because one of the variavbles causes the other, or whether they perhasps are related for some other reason.  Watch the chapter 6 videos from the GeorgeTown videos collection.!-->

The P-value is 0.000236 which means that two out of 10000 times we will get a result that the null hypothesis is true. We won't believe this hypothesis to be true since it happens so infrequently, so we will reject the null hypothesis. To further explain what we're seeing, the results of the TukeyHSD test shows that the WORDSUM test between LT high school and graduates are very different. Also, there's high school and graduates are different too. There is no other Significant differences between the average than those two stated.